Robots, Are They Overlords or Serf-Laborers?

### 2015-06-08 draft1.tex
Type in-class synthesis paper

>>>>

Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot. Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA(rod) exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue. The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par
The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients. However, these two prominent terms of technology closely resembles another, the Internet. As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies. Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.
